Loneliness

### 2023-02-20 docsrc/documentation/notebooks/loneliness.Rmd

---
title: "Loneliness"
output: html_document
bibliography: 
  - "refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
---

# Loneliness

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

## References

>>>>

---
title: "Loneliness"
output: html_document
bibliography: 
  - "docsrc/refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
---

## Loneliness

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

@@

```{r load_data, include=FALSE}
source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
```

### Methods

@@

```{r loneliness_data}
discrete_barplot("data/transitions/loneliness/clm/loneliness_2018_2019.rds", 'next_loneliness')
```

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("data/transitions/loneliness/clm/loneliness_2018_2019.rds", "next_loneliness") 
clm_output("data/transitions/loneliness/clm/loneliness_2018_2019.rds")
```

### References
